\vspace{-10pt}Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-17pt}

### 2019-09-22 paper/main.tex
System model and into on first page

\title{Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-10pt}}

@@

 \author{\authorblockN{Agrim Gupta, Pranav Sankhe, Kumar Appaiah, Manoj Gopalkrishnan}
 \
 \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay\\
 \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in \vspace{-15pt}}
% \thanks{Parts of this work was supported by the Bharti Centre for Communication in
% IIT Bombay, and the Visvesvaraya
% PhD Scheme of Ministry of Electronics \& Information Technology,
% Government of India (implemented by the Digital India Corporation).
% }}
}
\maketitle

@@

  % \noindent We consider problem of quantization and interpolation of
  % time and frequency varying precoding matrices in wireless MIMO
  % systems. Knowledge of precoder matrices at the transmitter can We first establish a result comparing the performance of
  % quantization and interpolation attempted directly over the Stiefel
  % manifold rather than over the Unitary manifold, as has been the
  % primary approach thus far. We propose a predictive quantization
  % algorithm to improve upon the quantization metric by exploiting both
  % time and frequency correlations in a constructed frequency hopping
  % scenario. Building upon these, we finally propose a joint
  % time-frequency interpolating algorithm to estimate the precoders
  % which were not fed back. We demonstrate significant improvements in
  % both BER curve and log-sum rate capacity over the existing
  % approaches.
\begin{abstract}

@@

\vspace{-6pt}
\section{Introduction}
\vspace{-6pt}
\label{intro}
% Broad summary of your work, come to your problem definition.
% Can remove MIMO wireless systems
In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit vector that corresponds to the signal emanating from the $N_T$ transmit antennas.
The precoding matrix used to maximize the achievable rate using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
However, since the MIMO channel matrix is estimated at the receiver, the transmitter requires receiver feedback for optimal precoding.
Therefore, the receiver needs to quantize and feed back the precoders while respecting the bit budget imposed by limited feedback schemes.
Given the high dimensionality of precoders (which form a $N_T \times N_R$ complex-valued matrix, viz. $2N_TN_R$ real numbers), effective quantization with just a few bits poses a significant challenge.

% Elaborate on each point (what people have done before) lecunnas
Past work has used two inherent properties of the precoders to enable effective quantization with just a few bits.
First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
Utilizing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
This improvement is obtained because of feeding back just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
% Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.

@@

\section{System Model}
\label{section2}
We consider a $N_T\times N_R$ MIMO-OFDM wireless system with $N$ subcarriers, and assume $N_T > N_R$ and $N_s = N_R$.
Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is,
\begin{equation}
\by_{i,t}=\bH^{H}_{i,t}\tilde{\bU}_{i,t}\bx_{i,t}+ \bw_{i,t}
\end{equation}
Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the point-to-point MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d. complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance. For this work, we assume that $\bH^{H}_{i,t}$ is estimated exactly, with zero error at the receiver.

>>>>

\title{\vspace{-10pt}Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework \vspace{-17pt}}

@@

 \author{\authorblockN{Agrim Gupta, Pranav Sankhe, Kumar Appaiah, Manoj Gopalkrishnan}
 \
 \authorblockA{Department of Electrical Engineering, Indian Institute of Technology Bombay\\
 \{agrim,pranavs,akumar,manojg\}@ee.iitb.ac.in \vspace{-18pt}}
% \thanks{Parts of this work was supported by the Bharti Centre for Communication in
% IIT Bombay, and the Visvesvaraya
% PhD Scheme of Ministry of Electronics \& Information Technology,
% Government of India (implemented by the Digital India Corporation).
% }}
}
\maketitle

@@

  % \noindent We consider problem of quantization and interpolation of
  % time and frequency varying precoding matrices in wireless MIMO
  % systems. Knowledge of precoder matrices at the transmitter can We first establish a result comparing the performance of
  % quantization and interpolation attempted directly over the Stiefel
  % manifold rather than over the Unitary manifold, as has been the
  % primary approach thus far. We propose a predictive quantization
  % algorithm to improve upon the quantization metric by exploiting both
  % time and frequency correlations in a constructed frequency hopping
  % scenario. Building upon these, we finally propose a joint
  % time-frequency interpolating algorithm to estimate the precoders
  % which were not fed back. We demonstrate significant improvements in
  % both BER curve and log-sum rate capacity over the existing
  % approaches.

\begin{abstract}

@@

\vspace{-5pt}
\section{Introduction}
\vspace{-5pt}
\label{intro}
% Broad summary of your work, come to your problem definition.
% Can remove MIMO wireless systems
In MIMO wireless systems, precoding matrices are used for transformation of an $N_S$-dimensional ($N_S \leq \text{min}(N_T,N_R))$ data stream onto an $N_T$-dimensional transmit signal.
The precoding matrix used to maximize the achievable rate using optimal power allocation is obtained via the SVD of the MIMO channel matrix \cite{love2008overview}.
However, since the MIMO channel matrix is estimated at the receiver, the transmitter requires receiver feedback for optimal precoding.
Therefore, the receiver needs to quantize and feed back the precoders while respecting the bit budget imposed by limited feedback schemes.
Given the high dimensionality of precoders (which form a $N_T \times N_R$ complex-valued matrix, viz. $2N_TN_R$ real numbers), effective quantization with just a few bits poses a significant challenge.

% Elaborate on each point (what people have done before) lecunnas
Past work has used two inherent properties of the optimal precoders to enable effective quantization with just a few bits.
First, the optimum precoders are not actually $2N_TN_R$ dimensional entities, but have an underlying manifold structure that allows to work with effective lower dimensions, when performing operations over the manifold directly \cite{pitaval2013codebooks}.
Second, these precoders are correlated in both time and frequency \cite{Gupt1905:Predictive}.
Utilizing the available correlations permit the use of predictive quantization algorithms, which enable improvement of the quantization error with time.
This improvement is obtained because of feeding back just the small extra information needed on top of the past fed back precoders, as compared to the new precoder information in the entirety.
% Exploiting frequency correlations permits the use of interpolation algorithms, which reduce the feedback overhead in a single OFDM frame, by feeding back CSI only for certain subcarriers, and interpolating over the others.

@@

\vspace{-3pt}
\section{System Model}
\label{section2}
We consider a $N_T\times N_R$ MIMO-OFDM wireless system with $N$ subcarriers, and assume $N_T > N_R$ and $N_s = N_R$.
Consistent with notation in \cite{6891198,Gupt1905:Predictive}, the data stream received on the $i$-th subcarrier, $t$-th time instant (or the $t$-th OFDM frame) is,
\begin{equation}
\by_{i,t}=\bH^{H}_{i,t}\tilde{\bU}_{i,t}\bx_{i,t}+ \bw_{i,t}
\end{equation}
Here, $\tilde{\bU}_{i,t} \in \mathbb{C}^{N_T \times N_R}$ is the quantized estimate of precoding matrix, $\by_{i,t} \in \mathbb{C}^{N_R \times 1}$ is the received data stream, $\bx_{i,t} \in \mathbb{C}^{N_T \times 1}$ denotes the transmitted signal, $\bH_{i,t} \in \mathbb{C}^{N_T \times N_R}$ denotes the point-to-point MIMO channel matrix and $\bw_{i,t}$ denotes the i.i.d. complex Gaussian noise with $\bw_{i,t} \sim \mathcal{N}_{\mathbb{C}}(0,N_0\bI_{N_R})$, $N_0$ being the noise variance. For this work, we assume that $\bH^{H}_{i,t}$ is estimated exactly, with zero error at the receiver.
